Generative Adversarial Networks

### 2017-12-02 cs6735/project/draft.tex
finished inference models

\subsection{Convolutional GANs}
Although convolutional neural networks (CNNs) seem well suited for the image generation tasks associated with GANs, difficulties associated with training initially constrained the use of convolutional models for both the discriminator and generator \citep{2017arXiv171007035C}. When implementing standard CNNs, one is often is unable to generate the same level of capacity and representational power. One solution proposed by Denton \textit{et al.} made use of Laplacian pyramids (LAPGAN), a type of image representation which repeatedly smooths and downsamples an image forming a sort of pyramid of images. At each layer of the pyramid, a conditional convolutional GAN is trained given generator output of the above layer. Another solution to this problem was proposed by Radford \textit{et al.}  simply made alterations to the existing deep convolutional network architecture \citep{2015arXiv151106434R}. Max pooling is replaced with strided layers within the discriminator and fractionally-strided layers within the generator. Furthermore, LeakyReLUs are used for all layers of the discriminator in place of the standard ReLU non-linearity function. The fractionally strided convolutions replicate within the generator replicate the benefits of the progressive upscaling within the Laplacian pyramid. The strided layers allow both the generator and discriminator to learn both the down-sampling and up-sampling operators during training \citep{2017arXiv171007035C}. Their architecture, called DCGAN, has become the base model for most GANs today \citep{2017arXiv170100160G}.

@@

\subsection{Inference GANs}
The first GAN architectures lacked methods to convert

\subsection{Progressive GANs}

>>>>

\subsection{Convolutional GANs}
Although convolutional neural networks (CNNs) seem well suited for the image generation tasks associated with GANs, difficulties associated with training initially constrained the use of convolutional models for both the discriminator and generator \citep{2017arXiv171007035C}. When implementing standard CNNs, one is often is unable to generate the same level of capacity and representational power. One solution proposed by Denton \textit{et al.} made use of Laplacian pyramids (LAPGAN), a type of image representation which repeatedly smooths and downsamples an image forming a sort of pyramid of images. At each layer of the pyramid, a conditional convolutional GAN is trained given generator output of the above layer.

Another solution to this problem was proposed by Radford \textit{et al.}  simply made alterations to the existing deep convolutional network architecture \citep{2015arXiv151106434R}. Max pooling is replaced with strided layers within the discriminator and fractionally-strided layers within the generator. Furthermore, LeakyReLUs are used for all layers of the discriminator in place of the standard ReLU non-linearity function. The fractionally strided convolutions replicate within the generator replicate the benefits of the progressive upscaling within the Laplacian pyramid. The strided layers allow both the generator and discriminator to learn both the down-sampling and up-sampling operators during training \citep{2017arXiv171007035C}. Their architecture, called DCGAN, has become the base model for most GANs today \citep{2017arXiv170100160G}.

@@

\subsection{Inference GANs}
The first GAN architectures lacked the ability to map an sample $\bm{x}$ to the associated latent vector $\bm{z}$. This feature of GANs is often referred to as an inference mechanism \citep{2017arXiv171007035C}. In 2016, two new architecture were independently proposed which introduce an adversarial learned inference by proposing the addition of another generator network \citep{2016arXiv160509782D, 2016arXiv160600704D}. The paper by Dumoulin \textit{et al.} proposes a network which learns the mapping of $\bm{x}$ to $\bm{z}$ and generates a set of continuous variables. For example, if the vector $\bm{z}$ is of length $n$, then $n$ means and $n$ variances will be generated. This allows for a probability distribution for each value of $\bm{z}$. Furthermore, the discriminator is now trained upon both a sample $\bm{x}$ and latent space vector $\bm{z}$ and has to discriminate between a real and fake pairs. The reconstructed images remain of poor quality \citep{2017arXiv171007035C}.
